### 2018-08-24 analysis-note-vf/Appendix.tex
push the results for the 4D binning of the incoherent dvcs
more updates to the appendix

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
   \beta$ & $\chi^{2}$\\
\hline
0.238  & 1.89 & 0.14 & 0.243 & 0.013 & -0.02 & 0.09 & 1.0\\
\hline
0.249  & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09 & 1.3\\
\hline
0.249  & 1.95 & 0.49 & 0.200 & 0.026 & -0.36 & 0.15 & 1.3\\
\hline
0.248  & 1.94 & 0.77 & 0.172 & 0.035 & 0.01 &  0.31 & 0.3\\
\hline
\end{tabular}
   \caption{free proton DVCS $Q^{2}$ and $x_{B}$ bins
   \ref{fig:ic_alpha_beta_fitting}.}
\label{Table:freeproton-t_bins}
\end{center}
\end{table}

@@

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
   \beta$ & $\chi^{2}$\\
\hline
0.177 & 1.56 & 0.14 & 0.19 & 0.009 & -0.03 & 0.12  & 2.3\\
\hline
0.249 & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09  & 1.3\\
\hline
0.345 & 2.64 & 0.30 & 0.269 & 0.019 & 0.29 & 0.15  & 0.3\\
\hline
0.471 & 3.34 & 0.78 & 0.262 & 0.052 & -0.23 & 0.25  & 0.9\\
\hline
\end{tabular}
   \caption{free proton DVCS $Q^{2}$ and $x_{B}$ bins
   \ref{fig:ic_alpha_beta_fitting}.}
\label{Table:freeproton-x_Q2_bins}
\end{center}
\end{table}

>>>>

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
   \beta$ & $\chi^{2}$\\
\hline
0.238  & 1.89 & 0.14 & 0.243 & 0.013 & -0.02 & 0.09 & 1.0\\
\hline
0.249  & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09 & 1.3\\
\hline
0.249  & 1.95 & 0.49 & 0.200 & 0.026 & -0.36 & 0.15 & 1.3\\
\hline
0.248  & 1.94 & 0.77 & 0.172 & 0.035 & 0.01 &  0.31 & 0.3\\
\hline
\end{tabular}
   \caption{Free proton DVCS published asymmetries associated with the 
   incoherent -t bins.}
\label{Table:freeproton-t_bins}
\end{center}
\end{table}

@@

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
   \beta$ & $\chi^{2}$\\
\hline
0.177 & 1.56 & 0.14 & 0.190 & 0.009 & -0.03 & 0.12  & 2.3\\
\hline
0.249 & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09  & 1.3\\
\hline
0.345 & 2.64 & 0.30 & 0.269 & 0.019 & 0.29 & 0.15  & 0.3\\
\hline
0.471 & 3.34 & 0.78 & 0.262 & 0.052 & -0.23 & 0.25  & 0.9\\
\hline
\end{tabular}
   \caption{Free proton DVCS published asymmetries associated with the 1250 
   incoherent $Q^{2}$ and $x_{B}$ bins.}
\label{Table:freeproton-x_Q2_bins}
\end{center}
\end{table}

\begin{figure}[tp]
\centering
\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results using 
   the interpolation method to get the free proton asymmetries at our kinematic 
   , the red squares are our results using the method of tuning our kinematics 
   to get kinematics similar to the published free proton from E1DVCS1 
   experiment. The gray band stands for the systematic errors calculated as the 
   difference between the two extraction methods. The green circles are the 
   HERMES inclusive measurement \cite{HERMES_BSA} results. The blue and red 
   curves are from an on-shell calculations from S.  Liuti and K.  Taneja 
   \cite{simonetta_2}. The solid and dashed black curves are from the off-shell 
   calculations \cite{EMC_vadim_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}
